### 2023-07-17 content/submission/plos_revision1/answer_to_reviewers.md

> Use the full words, rather than abbreviations, in figure legends for clarity.

Abbreviations in the legends have been written-out (except SI units).
Additionally we added a bit of background information on the specimen to the legend of Fig. 1.

> In the discussion section, the authors mentioned acquiring high-resolution tomographic datasets of a large collection of cichlids.
> However, the statement that "the acquired datasets were imaged over a wide-spanning range of voxel size (3.5–50 μm)" is incorrect.
> The voxel size is specimen-specific, depending on the size of the fish and the chosen parameters.
> Please clarify this point to accurately represent the imaging process.
> The finest resolution was obtained only for small fishes, so specific structures of a fish will have the same image resolution throughout the entire specimen.

The statement over the 'wide-spanning range of voxel sizes' is *not* incorrect, at most---if applied to *one* specimen---imprecise.
The range of voxel sizes is true for the whole study, while---as also correctly noted by the reviewer---the voxel size is specimen- or scan-specific.
We have added a bit of explanatory text to both the materials and discussion section.

@@

> It would be beneficial to include references in the discussion section to support the arguments and provide a broader context for the findings.

The main scientific 'use case' of the method focuses on the automated, non-destructive extraction of the otolith volume from the tomographic data.
To the best of our knowledge, our manuscript is the first to describe such a method.
We have found two references describing otoliths or otolith structure, both on explanted otoliths.
We have added those to the discussion section.

### 2023-07-17 content/submission/plos_revision1/answer_to_reviewers.md

---
title: Answer to reviewers of PONE-D-23-10896 (Microtomographic investigation of a large corpus of cichlids)
author: David Haberthür
date: 17.7.2023
---

### 2023-07-17 manuscript.tex
Comment otolith extraction notebook [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/1f10c12e87d556170c61c2bcd4900dcecb5035ed.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/1f10c12e87d556170c61c2bcd4900dcecb5035ed/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5577126248

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a690fe23582f53c283f038e12d0f163b7ffa128a}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/a690fe23582f53c283f038e12d0f163b7ffa128a/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/a690fe23582f53c283f038e12d0f163b7ffa128a}{habi/EAWAG-manuscript@a690fe2}
on July 14, 2023.

@@

@@

We thank Salome Mwaiko for taking care of the fish collection at Eawag and Mark Charran for helping to find suitable specimens to represent each species.
We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{36}{]} for helping us write this manuscript collaboratively.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{OpenSCAD. {[}cited 14 Jul 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 14 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al. Open collaborative writing with Manubot. Schneidman-Duhovny D, editor. PLoS Comput Biol. 2019;15: e1007128. doi:\href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...1f10c12e87d556170c61c2bcd4900dcecb5035ed}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/1f10c12e87d556170c61c2bcd4900dcecb5035ed/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/1f10c12e87d556170c61c2bcd4900dcecb5035ed}{habi/EAWAG-manuscript@1f10c12}
on July 17, 2023.

@@

To our best knowledge, no fully automated method for non-destructive otolith extraction from high-resolution tomographic data has been published up to now.
Vasconcelos-Filho et al.~{[}doi:10.3389/fmars.2019.00728{]} show a potentially objective method to count growth rings in otoliths of six fish species, but performed their study on extracted otoliths ``embedded in a styrofoam cube'', while our method non-destructively extracts the otoliths from the tomographic data.
Gu et al. {[}\protect\hyperlink{ref-HYXdLQTV}{36}{]} also provide detailed insight into otolith and combine microtomographic imaging (with unknown voxel size) with scanning electron microscopy, but also mention that the ``otoliths were removed {[}from \emph{Bahaba taipingensis}{]}, cleaned and kept dry for morphologic observation''.

@@

We thank Salome Mwaiko for taking care of the fish collection at Eawag and Mark Charran for helping to find suitable specimens to represent each species.
We are grateful to the \href{https//www.mic.unibe.ch/}{Microscopy Imaging Center} of the University of Bern for the infrastructural support.
We thank the \texttt{manubot} project {[}\protect\hyperlink{ref-YuJbg3zO}{37}{]} for helping us write this manuscript collaboratively.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{OpenSCAD. {[}cited 17 Jul 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 17 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 17 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-HYXdLQTV}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Gu Y-G, Huang H-H, Liang Y, Fang Y, Dai M, Ou Y-J, et al. Micro-CT and SEM investigation of sound absorption structure and chambers in the otoliths of Giant Panda fish species - Chinese Bahaba (Bahaba taipingensis). Micron. 2022;161: 103342. doi:\href{https://doi.org/10.1016/j.micron.2022.103342}{10.1016/j.micron.2022.103342}}

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{Himmelstein DS, Rubinetti V, Slochower DR, Hu D, Malladi VS, Greene CS, et al. Open collaborative writing with Manubot. Schneidman-Duhovny D, editor. PLoS Comput Biol. 2019;15: e1007128. doi:\href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128}}
